---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: "Times New Roman", serif;
  text-align: center;
  background-color: #eef7ff;

}

h1{
text-align: center;
text-decoration: underline;
}

h2{
text-align: center;
text-decoration: underline;
}

img{
  display: block;
  margin: auto;
  width: 50%;
}


```

# The effect of hunger on the speed of aiming
This study is tracking the affect that hunger has on the speed of aiming using the aim trainer on Human Benchmark. The form was to be completed 2 times every time the subject was going to eat, once before, and once after.


```{r}
library(tidyverse)
# reading csv
logged_data.df <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRkJgjwYTm6WlE0DzkXeaLbayxUL80OZ3k5HTGtOnFZpxy2V_54C-Qb_JTSXnyVVXxmJZ6FndIHKnmr/pub?output=csv")

# renaming variables
latest_data.df <- logged_data.df %>%
  rename(recently_eaten = 2,
         how_hungry = 3,
         aim_speed = 4)

#summary values
# maximum and minimum aim speed
max_speed <- max(latest_data.df$aim_speed)
min_speed <- min(latest_data.df$aim_speed)
# mean of values in aim speed variable
mean_speed <- mean(latest_data.df$aim_speed)
#how many values
length <- length(latest_data.df$aim_speed)

```
## Summary Statistics
The mean aim speed is `r round(mean_speed, 2) `.

The minimum recorded aim speed is `r min_speed` and the maximum recorded aim speed is `r max_speed`. This gives a range of `r round(max_speed - min_speed, 2)`.

There are `r length` values recorded in this study.

# Bar Charts
## Aim speed bar chart
```{r}
# aim speed bar chart
ggplot(data = latest_data.df) +
  geom_bar(aes(x = aim_speed),
           fill = "#0000FF")
```

The bar chart shows the range of aim speeds that were recorded during the study

## Aim speed based on whether or not someone has eaten
```{r}
# aim speed based on eaten recently or not
ggplot(data = latest_data.df) +
  geom_bar(aes(x = aim_speed, fill = recently_eaten))
```

The bar chart shows the recorded aim speeds colored based on whether or not the subject had recently eaten. We can see that when the subject had eaten in the last 30 minutes before completing the form, their aim speeds tend to be lower than when they hadn't eaten recently.

